\Large Generative Dynamics of Supreme Court Citations

### 2018-05-08 Tex/paper.tex
added information about agreement between Fowler and Courtlistener

 \section{Empirical Analysis}
Our three data sources for this study include the Supreme Court Database (SCDB) \citep{spaeth2014supreme}, Martin-Quinn scores \citep{martin2002dynamic}, and Supreme Court citation data provided by the CourtListener Free Law Project \citep{CourtListener}. In the next section we explain the variables we construct using these data sources. We limit the Supreme Court terms included in our analysis to those that are covered by all three of these data source (1937--2015)\footnote{There were 145 cases that were listed in the SCDB but could not be matched to a case in the CourtListener data. We decided to exclude these 145 cases from our analysis}. The Supreme Court citation network from $1937 - 2015$ consists of $9,945$ cases. The breakdown of the data by the Court's Chief Justice is presented in Table \ref{tab:chiefs}. The network has a total of $111,986$ citation ties.\footnote{In order to focus on citation actions that were not intended to totally invalidate an opinion, we exclude $315$ citations that caused the cited case to be overruled. The data on overruling citation came from \citet{senate2016constitution}. Our results are virtually unchanged if we include the overruling citations.} The in- and outdegree distributions (i.e., the distributions of the number of citations sent and received by cases, respectively), are visualized in Figure \ref{degree_dist}. The maximum indegree (i.e., number of cases citing to a case) is $230$ and the maximum outdegree (i.e., number of cases cited by a case) is $162$. The majority of cases cite to and/or are cited by twenty or fewer other cases.

@@

>>>>

 \section{Empirical Analysis}
Our three data sources for this study include the Supreme Court Database (SCDB) \citep{spaeth2014supreme}, Martin-Quinn scores \citep{martin2002dynamic}, and Supreme Court citation data provided by the CourtListener Free Law Project \citep{CourtListener}. In the next section we explain the variables we construct using these data sources. We limit the Supreme Court terms included in our analysis to those that are covered by all three of these data source (1937--2015)\footnote{There were 145 cases that were listed in the SCDB but could not be matched to a case in the CourtListener data. We decided to exclude these 145 cases from our analysis. Additionally, since the most commonly used data on Supreme Court citations in political science come from \citet{fowler2007network}, we compared the Fowler data to the CourtListener data in the time interval that they overlap (1937--2001). We found considerable agreement---over 95\% of the citations recorded in the CourtListener dataset were also in the Fowler dataset, and over 96\% of the citations recorded in the Fowler data were also in the CourtListener dataset.}. The Supreme Court citation network from $1937 - 2015$ consists of $9,945$ cases. The breakdown of the data by the Court's Chief Justice is presented in Table \ref{tab:chiefs}. The network has a total of $111,986$ citation ties.\footnote{In order to focus on citation actions that were not intended to totally invalidate an opinion, we exclude $315$ citations that caused the cited case to be overruled. The data on overruling citation came from \citet{senate2016constitution}. Our results are virtually unchanged if we include the overruling citations.} The in- and outdegree distributions (i.e., the distributions of the number of citations sent and received by cases, respectively), are visualized in Figure \ref{degree_dist}. The maximum indegree (i.e., number of cases citing to a case) is $230$ and the maximum outdegree (i.e., number of cases cited by a case) is $162$. The majority of cases cite to and/or are cited by twenty or fewer other cases.

@@

We include a dependence term to account for each of the dynamics that we hypothesize will characterize the Supreme Court Citation Network---transitivity, reciprocity, popularity, and activity. We expect that the coefficients associated with each of these dependence effects will be positive. The dependence effect included in the model to account for transitivity is the count of the number of triangles in $C_{\leq t}$. The log odds interpretation of the triangle statistic is that  $\theta$ gives the change in the log odds of case $i$ citing case $j$ associated  with each additional triangle that would be created by case $i$ citing case $j$ (e.g., if opinions in cases $i$ and $j$ cite one common case $k$, the log odds that case $i$ cites case $j$ change by theta relative to the configuration in which cases $i$ and $j$ do not cite any of the same cases).

The statistic included in the model for reciprocity counts the number of mutual dyads (i.e., dyads in which cases $i$ cites case $j$, and case $j$ cites case $i$) in $C_{\leq t}$. In practice, this is the number of mutual dyads in $C_{\leq t}$, since mutual dyads must emerge among opinions that were written in the same term.The log odds interpretation of the reciprocity term is that $\theta$ gives the change in the log odds of a tie

  \subsubsection{Dynamics in effects}
